### 2017-02-02 local-capability-machine.tex
missing $
removed n' < n requirement from memSat
Had forgotten to change a n' i previous commit
Added proof of memsat downwards closure

\begin{align*}
  &\memSatPar{\ms}{W}{P}
    \text{ iff }
    \left\{\begin{aligned}
        &\hs = \biguplus_{r\in\activeReg{W}}P(r) \land \\
        &\forall r \in \activeReg{W} \ldotp\\
        &\quad  \forall n'<n \ldotp \\
        &\qquad \exists H,s \ldotp\\
        &\qquad \quad W(r) = (\_,s,\_,\_,H) \land \\
        &\qquad \quad \npair[n']{P(r)} \in H(s)(\xi^{-1}(W))\\
      \end{aligned}\right.
\end{align*}
\dominique{quantification over $n' < n$ needed?}

@@

\begin{lemma}[Heap satisfaction downwards closure]
  \label{heap-sat-dc}
  \begin{align*}
    &\forall \hs, n' \leq n, W \ldotp \\
    &\quad \heapSat[\hs]{n}{W} \Rightarrow \heapSat[\hs]{n'}{W}
  \end{align*}
\end{lemma}

@@

      Step~\ref{step:ip-non-zero}.\dominique{TODO: check.  What about ms_f and other stuff.}

>>>>

\begin{align*}
  &\memSatPar{\ms}{W}{P}
    \text{ iff }
    \left\{\begin{aligned}
        &\hs = \biguplus_{r\in\activeReg{W}}P(r) \land \\
        &\forall r \in \activeReg{W} \ldotp\\
        &\quad \exists H,s \ldotp\\
        &\qquad W(r) = (\_,s,\_,\_,H) \land \\
        &\qquad \npair[n]{P(r)} \in H(s)(\xi^{-1}(W))\\
      \end{aligned}\right.
\end{align*}
\dominique{quantification over $n' < n$ needed?}

@@

\begin{lemma}[Heap satisfaction downwards closure]
  \label{lem:heap-sat-dc}
  \begin{align*}
    &\forall \hs, n' \leq n, W \ldotp \\
    &\quad \heapSat[\hs]{n}{W} \Rightarrow \heapSat[\hs]{n'}{W}
  \end{align*}
\end{lemma} 
\begin{proof}[Proof of Lemma~\ref{lem:heap-sat-dc}]
  Let $\ms$, $n' \leq n$, and $W$ be given and assume
  \[
    \heapSat[\hs]{n}{W}
  \]
  This assumption gives us $P : \activeReg{W} \fun \MemSegments$ such that
  \begin{enumproof}
    \item $\hs = \biguplus_{r\in\activeReg{W}}P(r)$ \label{pf:heap-sat:prop1}
    \item \label{pf:heap-sat:prop2}
      \begin{align*}
        &\forall r \in \activeReg{W} \ldotp\\
        &\quad \exists H,s \ldotp\\
        &\qquad W(r) = (\_,s,\_,\_,H) \land \\
        &\qquad \npair[n']{P(r)} \in H(s)(\xi^{-1}(W))
      \end{align*}
  \end{enumproof}
  Using $P$ as witness, \ref{pf:heap-sat:prop1} is the first condition we need. Now let $r$ be given and use \ref{pf:heap-sat:prop2} to get $H$ and $s$ such that
  \begin{enumproof}[resume]
    \item $W(r) = (\_,s,\_,\_,H)$ 
    \item $\npair[n]{P(r)} \in H(s)(\xi^{-1}(W))$ \label{pf:heap-sat:interp}
  \end{enumproof}
We now need to show
\[
        \npair[n']{P(r)} \in H(s)(\xi^{-1}(W))
\]
which follows from \ref{pf:heap-sat:interp}, $n' \leq n$, and $H(s)(\xi^{-1}(W))$ is a $\UPred{\MemSegments}$.
\end{proof}

@@

      Step~\ref{step:ip-non-zero}.\dominique{TODO: check.  What about $ms_f$ and other stuff.}
